Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-05-16 AM+draft.tex
17 May morning commit - sim section

>>>>

The median run times for Eagle and the other computer programs across the six scenarios are shown in Figure 1. 
Eagle was significantly faster, sometimes by orders of magnitude,  than the other multiple-locus
 implementations, especially for the larger data sets. For a simulation study with 150 individuals and 
 5000 snp, Eagle produced results in seconds.  For the larger simulation scenarios 1500x50K and 350x400K, 
 analyses with Eagle took under two minutes. Even for data from a couple of thousand individuals and half a million 
 snp (2000x500K), the median run time of Eagle was under 14 minutes. For our scenarios where there 
 were thousands of individuals and 1.5 million snp, Eagle took just over two hours for the analysis of data from 
 4000x1.5M and just under 12 hours for the analysis of data from 10000x1.5M. However, the long run time for 10000x1.5M 
 is due, largely, to the extra processing required for having data larger than the memory capacity of the computer. 
 Towards the end of our simulation study, we gained access to a high memory computer with 512 Gigabytes of RAM. 
 We reran Eagle on data from the largest scenario 10000x1.5M to measure the impact on run time.  By increasing 
 the memory, the median run time dropped by almost half from 699.55 minutes to 413.23 minutes.
